---
title: "Favourite foods"
author: "Rebecca Smith"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(readxl)
install.packages("janitor")
library(janitor)
install.packages("readr")
library(readr)
```

## Exercise 1

* Read in the Excel file called `favourite-food.xlsx` from the `data-raw/` folder.

```{r read-file, eval=TRUE}
fav_food <- read_excel("data-raw/favourite-food.xlsx")
fav_food
```

* Clean up `NA`s and make sure you're happy with variable types.

```{r clean-up, eval=TRUE}
fav_food <- read_excel("data-raw/favourite-food.xlsx",
                       na = c("N/A", "99999"))%>%
  janitor::clean_names()

fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
  )

glimpse(fav_food)
```

* Convert SES (socio economic status) to a factor variables with levels in the 
following order: `Low`, `Middle`, `High`.

```{r convert-SES, eval=TRUE}
fav_food <- fav_food%>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
```

* Write out the resulting data frame to `favourite-food.csv` in the `data/` folder.

```{r write-in-folder, eval=TRUE}
write_csv(fav_food, file = "data/favourite-food.csv")
```

* Finally, read `favourite-food.csv` back in from the `data/` folder and 
observe the variable types. Are they as you left them?

```{r read-back-in, eval=TRUE}
favourite_food <- read_csv("data/favourite-food.csv")
```

## Exercise 2

* Read in the Excel file called `favourite-food.xlsx` from the `data-raw/` folder, 
taking care of `NA`s and variable types.

```{r read-in-excel, eval=TRUE}
fav_food <- read_excel("data-raw/favourite-food.xlsx",
                       na = c("N/A", "99999"))%>%
  janitor::clean_names()

fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
  )

glimpse(fav_food)
```

* Convert SES (socio economic status) to a factor variables with levels in the 
following order: `Low`, `Middle`, `High`.

```{r convert-SEs, eval=TRUE}
fav_food <- fav_food%>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
```

* Write out the resulting data frame to `favourite-food.rds` in the `data/` folder.

```{r write-rds, eval=TRUE}
write_rds(fav_food, file = "data/favourite-food.rds")
```

* Read `favourite-food.rds` back in from the `data/` folder and observe the 
variable types. Are they as you left them?

```{r read-rds, eval=TRUE}
favourite_food <- read_rds("data/favourite-food.rds")
Count(favourite_food)
```

## References {#references}
1. Assignment Adapted from [Mine Cetinkaya-Rundel's Data Science in a Box](https://github.com/rstudio-education/datascience-box)